---
title: "Modelling teacher burnout - non-linear extensions of SEM"
format: html
bibliography: bib.bib
---

``` {r Loading-packages}
#| code-fold: true
#| code-summary: "Loading R packages"
#| message: false
#| warning: false
library(tidyverse)
library(rio)
library(lavaan)
library(lavaanPlot)

# couldn't install "sleasy" package so copied code:
sem_structural_results <- function(model, nd = 3) {
  indic <- which(inspect(model, what = "std")$beta != 0,
                 arr.ind = TRUE, useNames = TRUE)

  result <- as.data.frame(cbind(
    colnames(inspect(model, what = "std")$beta)[indic[, 2]],
    colnames(inspect(model, what = "std")$beta)[indic[, 1]],
    round(inspect(model, what = "std")$beta[indic], digits = 3),
    round(inspect(model, what = "se")$beta[indic], digits = 3),
    round(pnorm(abs(inspect(model, what = "coef")$beta /
                      inspect(model, what = "se")$beta), lower.tail = FALSE)[indic], digits = 3)
  )
  )
  colnames(result) <- c("outcome", "predictor", "std estimate", "se", "p-value")

  return(result)
}
```

### The Dataset

The data examines the relationship between two aspects of teacher capacity with three aspects of teacher burnout. 

Teacher capacity: 

- Teacher Self Concept (TSC)
- Teacher Efficacy (TE)

Teacher burnout:

- Emotional Exhaustion (EE)
- Depersonalisation (DP)
- Reduced Personal Accomplishment (RPA)

Not included in the open dataset:

- Gender (619 male, 258 female)
- Experience (291 less than five years, 585 more than five years)

Originally published in the paper "[Teachers' burnout: A SEM analysis in an Asian context](https://www.sciencedirect.com/science/article/pii/S2405844019368033)" [@prasojoTeachersBurnoutSEM2020], and used as an example data set in @jongerlingStructuralEquationModeling2024, which is where the data is imported from:

``` {r}
#| code-summary: "Importing data"
dataset <- import("https://github.com/lamethods/data/raw/main/4_teachersBurnout/2.%20Response.xlsx") |> 
    as_tibble()
var_names <- colnames(dataset)
head(dataset |> select(TSC1, TSC1, TE1, DE1, EE1, RPA1))
```

Note that the data is not complete, @jongerlingStructuralEquationModeling2024 mention that gender was in the original dataset for the paper but not included (understandably) in the open dataset. 

``` {r}
#| include: false
# Saving data - just in case
saveRDS(dataset, "data/dataset.RDS")
```

# Initial SEM

Taken from @jongerlingStructuralEquationModeling2024. 

``` {r}
SEM_model <- '
# Regressing items on factors 
TSC =~ TSC1 + TSC2 + TSC3 + TSC4 + TSC5
TE =~ TE1 + TE2 + TE3 + TE5
EE =~ EE1 + EE2 + EE3 + EE4
DE =~ DE1 + DE2 + DE3
RPA =~ RPA1 + RPA2 + RPA3 + RPA4

# Relations between factors
TE ~ TSC
EE ~ TE + TSC
DE ~ TE + TSC
RPA ~ TE + TSC
'
```

``` {r}
#| include: false
set.seed(19)
ind <- sample(c(rep("model.building", 438), rep("holdout", 438)))
tmp <- split(dataset, ind)
model.building <- tmp$model.building
holdout <- tmp$holdout
```

``` {r}
fit.mlr <- sem(model = SEM_model, data = dataset, std.lv = TRUE,
              estimator = "MLR", meanstructure = TRUE)
# summary(fit.mlr, standardized = TRUE)
```

``` {r}
lavaanPlot(fit.mlr, coefs = TRUE)


```

This does not replicate the plot

# Extending

# References